Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
add fl change

\subsection{The Effects of Our Heuristics}
\label{subsec:effect-of-heuristics}
We evaluate the usefulness of (1) our information-theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in several different modes:\\[1ex]
\begin{tabulary}{\linewidth}{rL}
  \AnyOpt{}: & We ignore the information-theoretic preference metric entirely,
  returning the first lens \GreedySynth finds without using this information. \\ 
  \FLOpt{}: &  \GreedySynth uses the information-theoretic preference
  metric to find a lens, but only the original pair of stochastic
  regular expressions are considered as end-points.  \\
  \CCOpt{}: & We replace our information-theoretic cost metric with one where
              the cost of the lens is the number of disonnects plus the number
              of merges.\\
  \ZTOpt{}: & \ZTOpt{} runs the algorithm with the termination parameter
              universally set to 0 (default). \\
  \TFTOpt{}: & \TFTOpt{} runs the algorithm with the
               termination parameter universally set to 25. \\
  \NTFTOpt{}: & \NTFTOpt{} runs the algorithm with the
                termination parameter universally set to -25. \\
\end{tabulary}

>>>>

\subsection{The Effects of Our Heuristics}
\label{subsec:effect-of-heuristics}
We evaluate the usefulness of (1) our information-theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in several different modes:\\[1ex]
\begin{tabulary}{\linewidth}{rL}
  \AnyOpt{}: & We ignore the information-theoretic preference metric entirely,
               returning the first lens \GreedySynth finds without using this information. \\ 
  \FLOpt{}: &  \GreedySynth uses the information-theoretic preference
              metric to find a lens, and we return immediately upon finding a
              satisfying lens, instead of returning based on \Continue.  \\
  \CCOpt{}: & We replace our information-theoretic cost metric with one where
              the cost of the lens is the number of disonnects plus the number
              of merges.\\
  \ZTOpt{}: & \ZTOpt{} runs the algorithm with the termination parameter
              universally set to 0 (default). \\
  \TFTOpt{}: & \TFTOpt{} runs the algorithm with the
               termination parameter universally set to 25. \\
  \NTFTOpt{}: & \NTFTOpt{} runs the algorithm with the
                termination parameter universally set to -25. \\
\end{tabulary}
